Astropy - New software standards for a growing community

### 2017-09-20 main.tex
Update on Overleaf.
add outline

%% Reintroduced the \received and \accepted commands from AASTeX v5.2
%\received{July 1, 2016}
%\revised{September 27, 2016}

%% Command to document which AAS Journal the manuscript was submitted to.
%% Adds "Submitted to " the arguement.
\submitjournal{ApJ}

@@

\shorttitle{Astropy Project II}
\shortauthors{Astropy Project et al.}

@@

\draft{\today}

@@

@@

%\subsection{Difficulty of reversing design choices}
%Deciding if a feature should be included
%difficulty to decide where general use ends and "handy feature for some" starts, i.e. how to reject PRs or deal with maintenance burden

@@

start with short description of the astropy approach and features (JPL ephemerids, barycentric correction, proper motions, coordinate frames) then shows the tests. In particular, we had a discussion on problems with the definition of some coordinate system on the mailing list. Getting that discussion in here gives us a refereed paper to point to when we need to push the IAU to fix that.

@@

\subsection{Convolution}
Astropy implements `normalized convolution' \citep[e.g.,][]{Knutsson1993}, which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.   In version $<=1.3$, the direct convolution and fft convolution approaches were not consistent, with fft convolution implementing normalized convolution and direct convolution implementing a different approach.  As of v2.0, the two methods are consistent and include a suite of consistency checks.

@@

\section{Infrastructure for affiliated packages}
\subsubsection{Package template}
bsipocz may write this up if there is no other takers
\subsection{Continuous integration helpers}
bsipocz should write this up
\subsection{sphinx extensions}
probably Tom R should write this up
\section{State of the Ecosystem}

@@

\bibliographystyle{aasjournal}          
\bibliography{bibliography}

>>>>

%% Reintroduced the \received and \accepted commands from AASTeX v5.2
%\received{July 1, 2016}
%\revised{September 27, 2016}
\draft{\today}
%% Command to document which AAS Journal the manuscript was submitted to.
%% Adds "Submitted to " the arguement.
\submitjournal{ApJ}

@@

\shorttitle{\aastex\ Astropy Project II}
\shortauthors{Astropy Project et al.}

@@

@@

Difficulty of reversing design choices
Deciding if a feature should be included
difficulty to decide where general use ends and "handy feature for some" starts, i.e. how to reject PRs or deal with maintenance burden

@@

@@

The \texttt{astropy.coordinates} subpackage ...

- Three-tiered structure for coordinates: representation, frame, skycoord
- With differential classes, frames support velocities
- Celestial coordinates, and local coordinates (via EarthLocation + Time)
- JPL ephemerids

start with short description of the astropy approach and features (JPL ephemerids, barycentric correction, proper motions, coordinate frames) then shows the tests.

In particular, we had a discussion on problems with the definition of some coordinate system on the mailing list. Getting that discussion in here gives us a refereed paper to point to when we need to push the IAU to fix that.

@@

\subsection{Convolution}
Astropy implements `normalized convolution' (e.g., Knutsson and Westin 1993; http://ieeexplore.ieee.org/abstract/document/341081/), which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.   In version $<=1.3$, the direct convolution and fft convolution approaches were not consistent, with fft convolution implementing normalized convolution and direct convolution implementing a different approach.  As of v2.0, the two methods are consistent and include a suite of consistency checks.

@@

\section{Infrastructure for affiliated packages}
\subsubsection{Package template}
\subsection{Continuous integration helpers}
bsipocz should write this up
\subsection{sphinx extensions}
probably Tom R should write this up
\section{State of the Ecosystem}

@@

%\bibliographystyle{aasjournal}
%\bibliography{bibliography}
